### 2021-10-21 documentos/vector_space.tex
Typo en mis últimos comentarios

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$
\footnote{
We can further \cpnote{desmechar} the vector space, by identifying each index
$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
such that to each multindex  $\valpha$ there corresponds a binary string of 
length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
each of the $2N$ components. 
}. 
We can indeed restate \eref{eq:oplus}, an\janote{and?} say that for valid quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
For example, in \fref{fig:two:qubit:examples}(c) the indices that 
correspond to preserved components are 
$\valpha^{(0)} = (0,0)$, 
$\valpha^{(1)} = (0,2)$, 
$\valpha^{(2)} = (1,0)$, 
$\valpha^{(3)} = (2,2)$, and
$\valpha^{(4)} = (3,2)$. However, 
$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved and thus this 
diagram does not correspond to a quantum channel.  From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.

>>>>

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$
\footnote{
We can further \cpnote{desmechar} the vector space, by identifying each index
$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
such that to each multindex  $\valpha$ there corresponds a binary string of 
length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
each of the $2N$ components. 
}. 
We can indeed restate \eref{eq:oplus}, an\janote{and*?} say that for valid quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
For example, in \fref{fig:two:qubit:examples}(c) the indices that 
correspond to preserved components are 
$\valpha^{(0)} = (0,0)$, 
$\valpha^{(1)} = (0,2)$, 
$\valpha^{(2)} = (1,0)$, 
$\valpha^{(3)} = (2,2)$, and
$\valpha^{(4)} = (3,2)$. However, 
$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved and thus this 
diagram does not correspond to a quantum channel.  From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.
